% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2014 Drew Erny <drewerny@gmail.com> http://www.dperny.net
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\flushbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
%\setlength{\bmargin}{-0.3in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
  \newcommand{\resheading}[1]{\vspace{-2pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
      \begin{shaded}

        \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
      \end{shaded}
    }\vspace{-10pt}
  }

  \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}}

  %-----------------------------------------------------------
  \begin{document}

  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

    \textbf{\Large Drew Erny} & \textbf{\today} \\
    \texttt{drewerny@gmail.com} & \texttt{985 665-1284} \\
    \texttt{dperny.net} & \texttt{github.com/dperny}

  \end{tabular*}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \resheading{Skills}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}

    \item {\bf Development:} Ruby, Python, C, Java, Scheme, Rust (learning)

    \item {\bf Web:} HTML5/CSS3/Javascript, Ruby on Rails and PHP. 

    \item {\bf Software and Technology:} Strong understanding of Unix, bash, zsh, git, vim, and tmux. Some experience with AWS S3 and Cloudfront.

    \item {\bf Tutoring:} Run unofficial computer science study sessions and one-on-one tutoring for classmates, peers, and underclassmen.

      % \item Ability and passion for imparting technical concepts to non-technical people or novice programmers.

  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \resheading{Career Experience}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}

    \item
      \ressubheading{Nine (nine.is)}{Tuscaloosa, AL}{Software Engineer}{November 2013 - August 2014}
      \begin{itemize}
          \resitem{Performed full-stack development and maintenance of large-scale Ruby on Rails web applications for health care businesses, real estate agencies, and government.}
          \resitem{Maintained legacy PHP websites.}
          \resitem{Communicated technical concepts to nontechnical clients.}
      \end{itemize}

    \item
      \ressubheading{NSF Research Experience for Undergraduates}{Tuscaloosa, AL}{Software Engineering}{Summer 2013}
      \begin{itemize}
          \resitem{Designed and programmed educational modifications for teaching circuits at a college level using the popular video game Minecraft.}
          \resitem{Fleshed out and implemented finer details of higher-level design requirements provided by advisors.}
      \end{itemize}

    \item
      \ressubheading{Technology Assistant, Office of eTech}{Tuscaloosa, AL}{Student Technology Assistant}{January 2013 - April 2013}
      \begin{itemize}
          \resitem{Performed on and off site troubleshooting, repair, setup, and installation of hardware and software for the University of Alabama College of Arts \& Sciences.}
      \end{itemize}

  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \resheading{Projects}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}
    \item 
      \ressubheading{DayBreaker.co}{Startup Weekend Tuscaloosa}{https://github.com/MasterTasker/DayBreaker}{September 2014}
      \begin{itemize}
          \resitem{Led a team of professional and student developers to construct a time-management application.}
          \resitem{Built a functional prototype in two days.}
      \end{itemize}
    \item
      \ressubheading{dperny.net}{}{https://github.com/dperny/dperny.net}{November 2014}
      \begin{itemize}
          \resitem{Built totally custom site with Middleman and hosted on Github Pages.}
          \resitem{Extensively used latest web concepts such as semantic HTML5 and CSS3 flexboxes.}
          \resitem{Open-source and MIT licensed.}
      \end{itemize}
  \end{itemize}

  \pagebreak

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \resheading{Education}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}

    \item
      \ressubheading{The University of Alabama}{Tuscaloosa, AL}{B.S. Computer Science}{2012-2016 (expected)}
      \begin{itemize}
          \resitem{National Merit Finalist}
          \resitem{Engineering Leadership Scholarship recipient}
          \resitem{3.66 GPA}
      \end{itemize}
  \end{itemize}


  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \resheading{Leadership and Service Experience}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}

    \item
      \ressubheading{Head Judicial Officer}{}{The Mallet Assembly}{December 2013 - Present}
      \begin{itemize}
          \resitem{Maintained, revised, and rewrote the constitution for the longest continuously running honors program at the University of Alabama.}
          \resitem{Presided over disciplinary hearings and worked with University administration to uphold the student code of conduct.}
      \end{itemize}

    \item
      \ressubheading{Vice Chair}{}{Association for Computing Machinery, UA Student Chapter}{January 2013 - September 2013}
      \begin{itemize}
          \resitem{Coordinated guest industry events such as Microsoft appLab.}
          \resitem{Planned and executed chapter social events.}
      \end{itemize}

  \end{itemize}

  \end{document}

