% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2014 Drew Erny <drewerny@gmail.com> http://www.dperny.net
% (c) 2016 John Hossler <john.m.hossler@gmail.com> http://www.jmhossler.net
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\flushbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{1}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{1}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
%\setlength{\bmargin}{-0.3in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
  \newcommand{\resheading}[1]{\vspace{-2pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
      \begin{shaded}

        \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
      \end{shaded}
    }\vspace{-10pt}
  }

  \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}}

  \newcommand{\secondsubheading}[2]{
    \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
  \end{tabular*}\vspace{-6pt}}

  \newcommand{\basicsubheading}[1]{
    \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
      \textit{#1} \\
  \end{tabular*}\vspace{-6pt}}

  %-----------------------------------------------------------
  \begin{document}

  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\Large John Hossler} & \textbf{\today} \\
    \texttt{john.m.hossler@gmail.com} & \texttt{(205) 435-0986} \\
  \end{tabular*}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  % Objective
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{6mm}
  Motivated developer focused on improving developer experience and product quality. Looking to fill a Software Developer role
  to help deliver new products in a timely and confident fashion.

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Skillsets}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}
    \item {\bf Preferred Language:} Python
    \item {\bf Methodologies:} Agile, Clean Code, Clean Architecture, Pair Programming, SAFe, Behavior Driven Development, Test Driven Development
    \item {\bf Utilities:} kubernetes, ansible, git, docker, docker-compose, pytest, artifactory, jenkins, openstack, robot framework
  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Education}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}
    \item
      \ressubheading{The University of Alabama}{Tuscaloosa, AL}{B.S. Computer Science}{May 2018}
      \begin{itemize}
          \resitem{Engineering Leadership Scholarship recipient}
          \resitem{Presidential Scholarship recipient}
          \resitem{Minors:} Physics
      \end{itemize}
  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Career Experience}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}
    \item
      \ressubheading{Adtran}{Huntsville, AL}{Co-Op 1st Term}{May 2016 - August 2016}
      \begin{itemize}
          \resitem{Wrote scripts to standardize the company's existing automation libraries on PEP8 coding style.}
          \resitem{Reworked automation libraries to better utilize coding principles like inheritance, encapsulation, and DRY code.}
      \end{itemize}
      \secondsubheading{Co-Op 2nd Term}{Jan 2017 - August 2017}
      \begin{itemize}
          \resitem{Worked on test automation software to help with Continuous Integration goals in the company.}
          \resitem{Helped refactor existing packages to ease extension of functionality}
          \resitem{Participated and won documentation category in Hackathon event.}
      \end{itemize}
      \secondsubheading{Co-op 3rd Term}{August 2017 - December 2017}
      \begin{itemize}
          \resitem{Used Jenkins to automate the maintenance of permissions between Github
          Repositories and corresponding Jenkins Jobs.}
          \resitem{Worked on Artifactory configuration to aid in Continous Delivery}
          \resitem{Performed adminstration tasks on Jenkins, Artifactory, and Github.}
          \resitem{Participated and won 3rd Place in Hackathon event}
      \end{itemize}
      \secondsubheading{Full time}{June 2018 - Present}
      \begin{itemize}
          \resitem{Wrote automated tests for products to verify customer requirements.}
          \resitem{Improved and created Continous Integration and Continous Delivery tools to shorten the
          time from code submission to release.}
          \resitem{Maintained test infrastructure.}
          \resitem{Built tool for gathering metrics from developer environments across the globe.}
      \end{itemize}
  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Personal Projects}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}
    \item
      \basicsubheading{Group Study}
      \begin{itemize}
          \resitem{Organized and maintained book club for reading software engineering books.}
          \resitem{Organized study group for CCNA study group.}
      \end{itemize}
      \basicsubheading{Home lab}
      \begin{itemize}
          \resitem{Built a small local kubernetes cluster ran on a mixture of rasberry pis and old machines.}
          \resitem{Deployed gitlab along with gitlab runners to machines with docker-compose and ansible.}
      \end{itemize}
  \end{itemize}

\end{document}
